---
title: "Part 2: Revisiting the Titanic"
author: "Jess Robinson"
date: "May 13, 2019"
output: github_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r setup, include=FALSE}
#load libraries
library(tidyverse)
library(here)
library(knitr)
library(readr)
library(broom)
library(modelr)
library(caret)
library(rsample)

set.seed(1234)

theme_set(theme_minimal())
```

1. Load Data
------

```{r}
library(titanic)
titanic <- as_tibble(titanic_train) %>%
    mutate(as.factor(Survived))

kable(head(titanic)) 
```

2. Logistic Regression Models
------
## Predictions

*Age + Sex + Fare Model* 
```{r}
#create model 
agesexfare_mod<- glm(Survived ~ Age + Sex + Fare, data = titanic,
                           family = binomial)
#call summary
summary(agesexfare_mod)

```

*Class + Fare Model*
```{r}
#create model
classfare_mod<- glm(Survived ~ Pclass + Fare, data = titanic,
                           family = binomial)
#call summary
summary(classfare_mod)
```

*Age + Sex + Age/Sex Interaction Model*
```{r}
#create model
agesexint_mod<- glm(Survived ~ Age + Sex + Age*Sex, data = titanic,
                           family = binomial)
#call summary
summary(agesexint_mod)
```

## 10-fold validation
```{r}
#perform 10-fold cross-validation
titanic_results <- function(splits, i) {
  titanic_model <- glm(i, data = analysis(splits))
  titanic_holdout <- assessment(splits)
    res <- augment(titanic_model, newdata = titanic_holdout) %>%
    mutate(.resid = Survived - .fitted)
    res
}
library(rsample)
titanic_cv10  <- vfold_cv(data = titanic, v = 10) %>%
  mutate("Age + Sex + Fare" = map(splits, titanic_results, Survived ~ Age + Sex + Fare),
         "Fare + Class" = map(splits, titanic_results, Survived ~ Fare + Pclass),
         "Age + Sex + Age/Sex Interaction" = map(splits, titanic_results, Survived ~ Age + Sex + Age*Sex))  %>% 
  gather() %>% 
  unnest(statistic) %>% 
  group_by(model) %>% 
  summarise("Mean Square Estimate (MSE)" = mean(.resid^2, na.rm = TRUE)) 

kable(titanic_cv10)
```

Of the above models, Age + Sex + Fare has the lowest MSE, suggesting it is the best predictive model of the three.

#3. Random Forest Model
------
```{r}
#clean data
titanic_clean <- titanic %>%
  drop_na() %>%
  mutate(Survived = as.factor(Survived))

#random forest model 
fulltitanic_rf <- train(Survived ~ Pclass + Sex + Age + SibSp + Parch + Fare + Embarked, data = titanic_clean,
                    method = "rf",
                    ntree = 500,
                    trControl = trainControl(method = "oob"))

fulltitanic_rf 
```
## Variable Importance Plots
```{r}
#graph variable importance
randomForest::varImpPlot(fulltitanic_rf$finalModel)
```

The most important variable in predicting Titanic survival, according to the above chart, is sex.

##Out-of-Bag Error Rate
```{r}
#find OOB
fulltitanic_rf$finalModel
```

The OOB estimate of error rate is 18.77%.