---
title: 'Part 1: Trump'
author: "Jess Robinson"
date: "May 13, 2019"
output: github_document
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=6, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r setup, include=FALSE}
#load libraries
library(tidyverse)
library(here)
library(knitr)
library(readr)
library(broom)
library(modelr)
library(magrittr)
library(rsample)

set.seed(1234)

theme_set(theme_minimal())
```

## Import Data
```{r}
trump_data <- read_csv(here ("data", "trump.csv"))
```

Data comes from [the 2012 American National Election Studies survey](http://www.electionstudies.org/).

1. Basic Linear Regression
------

## Fitted Values
```{r}
#create linear regression model
video_mod <- lm(trump ~ video, data = trump_data)
#create data frame for fitted values
video_grid <-  trump_data %>%
  data_grid(video) 
#generate predicted value
video_grid <- augment(video_mod, newdata = video_grid)
kable(video_grid)
```

##Graph of Fitted Values
```{r}
#graph the fitted values
trump_data %>%
ggplot(mapping = aes(video)) +
  geom_point(aes(y = trump)) +
  geom_line(aes(y = .fitted), data = video_grid, color = "light blue", size = 1) +
  geom_point(aes(y = .fitted), data = video_grid, alpha = .1, color = "blue", size = 3) +
    labs(title = "Relationship between Video and Feelings Toward Trump",
       x = "Importance of the Video",
       y = "Warm Feelings toward Trump (Fitted)"
       )
```

## Statistical Signficance
```{r}
#call the summary stats
kable(tidy(video_mod))
kable(glance(video_mod))
```

There appears to be a strongly significant relationship between response to the video and attitudes towards Trump.
This model has a p-value of 0.
Importance of to the video explains approximately 48% of the variation in attitudes towards Trump.

2. Prediction
------
```{r}
#perform 10-fold corss-validation  
trump_results <- function(splits, i) {
  trump_model <- glm(i, data = analysis(splits))
  trump_holdout <- assessment(splits)
    res <- augment(trump_model, newdata = trump_holdout) %>%
    mutate(.resid = trump - .fitted)
    res
}

trump_cv10  <- vfold_cv(data = trump_data, v = 10) %>%
  mutate(demographic = map(splits, trump_results, trump ~ female + age + educ),
         party = map(splits, trump_results, trump ~ pid),
         full = map(splits, trump_results, trump ~ video + female + pid + age + educ))  %>% 
  gather() %>% 
  unnest(statistic) %>% 
  group_by(model) %>% 
  summarise("Mean Square Estimate (MSE)" = mean(.resid^2, na.rm = TRUE)) 

kable(trump_cv10)
```

Of the above models used, the one with the lowest MSE is the full model. 
This suggests the full model (which includes party ID, attitudes towards the video, age, education, sex), as compared with models that only take into account demographic characteristics (age, education, gender) or only party ID, best predicts warmth towards Trump. 